QPLIB: A Library of Quadratic Programming Instances

### 2018-02-04 QPLIB-3.tex
fix and update bibliography

Other quadratic instances were found in online libraries devoted to
specific QP problems as Max-Cut, Quadratic Assignment, Portfolio
Optimization, and several others. \textcolor{red}{In addition, we mention
that other generic libraries exist, e.g., 
Conic library CBLIB (\url{http://cblib.zib.de}) and 
MIPLIB 2010 (\url{http://miplib.zib.de/}), to mention just a few.}

>>>>

Other quadratic instances were found in online libraries devoted to
specific QP problems as Max-Cut, Quadratic Assignment, Portfolio
Optimization, and several others. \textcolor{red}{In addition, we mention
that other generic libraries exist, e.g., 
Conic library CBLIB (\url{http://cblib.zib.de}) and 
MIPLIB~2010 (\url{http://miplib.zib.de/}), to mention just a few.}\todo{AG: maybe cite CBLIB paper \cite{Friberg2016}}
